\Large UC President's Postdoctoral Fellowship Research Statement \\ \textbf{How Unique is the Solar System? Planetary Luminosities as Fingerprints for the Origins and Properties of Exoplanets}

### 2017-04-22 Postdoc Applications/AnaMariaPisoResume.tex
upd

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, Pegues, J., \& \"Oberg, K.I. \textit{The Role of Ice Compositions and Morphology For Snowlines and the C/N/O Ratios in Active Disks}. ApJ, accepted: arXiv:1611.00741  \\
\end{list2}

@@

\section{\sc Conferences and Seminars}

\begin{list2}
\item[] {\bf Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics} \\
iPLEX Lunch Seminar, Los Angeles, CA, September 2016\\
Invited talk \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
MIT Planetary Lunch Colloquium Series, Cambridge, MA, March 2016\\
Invited talk \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
CfA Small Scale Seminar, Cambridge, MA, February 2016\\
Invited talk \\
\end{list2}

@@

\begin{list2}
\item[] {\bf C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion} \\
Extreme Solar Systems III, Waikoloa Village, HI, December 2015 \\
Poster \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
University of Michigan Astronomy Lunch Talk, Ann Arbor, MI, November 2015 \\
Seminar speaker \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
University of Chicago Exoplanet Journal Club, Chicago, IL, November 2015 \\
Seminar speaker \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
MIT Exoplanet Tea, Cambridge, MA, October 2015 \\
Seminar speaker \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
Center for Integrative Planetary Science Planet and Star Formation Seminar, Berkeley, CA, September 2015 \\
Invited talk \\
\end{list2}

\begin{list2}
\item[] {\bf Minimum Core Masses for Giant Planet Formation} \\
CfA Exoplanet Pizza Lunch, Cambridge, MA, May 2015  \\
Internal department talk \\
\end{list2}

\begin{list2}
\item[] {\bf Minimum Core Masses for Giant Planet Formation} \\
Star and Planet Formation in the Southwest, Oracle, AZ, March 2015  \\
Contributed talk \\
\end{list2}

\begin{list2}
\item[] {\bf On the Minimum Core Mass for Giant Planet Formation} \\
CfA Exoplanet Pizza Lunch, Cambridge, MA, November 2013  \\
Internal department talk \\
\end{list2}

\begin{list2}
\item[] {\bf On the Minimum Core Mass for Giant Planet Formation} \\
Protostars and Planets VI, Heidelberg, Germany, July 2013  \\
Poster \\
\end{list2}

\begin{list2}
\item[] {\bf On the Minimum Core Mass for Giant Planet Formation} \\
IAUS 299: Exploring the Formation and Evolution of Planetary Systems, Victoria, BC, June 2013  \\
Contributed talk \\
\end{list2}

\begin{list2}
\item[] {\bf The Structure and Stability of Atmospheres Accreting around Protoplanetary Cores} \\
Exoplanets in Multi-body Systems in the Kepler Era, Aspen, CO, February 2013 \\
Poster \\
\end{list2}

@@

\vspace*{-.13in}
\begin{list2}
\item[] {\bf Exact relativistic viscous fluid solutions in NHEK background} \\
APS April Meeting, Washington, DC, February 2010  \\
Poster \\
\end{list2}

\vspace*{-.13in}
\begin{list2}
\item[] {\bf The Solar Wind}\\ 
Vienna Theory Lunch Club, TU Wien, Vienna, Austria, June 2009  \\
Invited talk \\
\end{list2}

>>>>

\item[] {\bf Organizer of UCLA iPLEX Lunch Talks } \hfill {\bf April 2017 - present}
\begin{list1}
\item[] Coordinator of weekly seminars in the Institute for Planets and Exoplanets \hfill \textit{Los Angeles, CA}
\end{list1}

\item[] {\bf Judge in the Los Angeles Basin EPS Student Research Symposium } \hfill {\bf April 2017}
\begin{list1}
\item[] Provided evaluations and feedback on science presentations by graduate and undergraduate students in Earth and Planetary Science \hfill \textit{Los Angeles, CA}
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, Pegues, J., \& \"Oberg, K.I. \textit{The Role of Ice Compositions and Morphology For Snowlines and the C/N/O Ratios in Active Disks}. ApJ, 2016, 833, 203  \\
\end{list2}

@@

\section{\sc Invited Talks}

\begin{list2}
\item[] {\bf The Role of Ice Compositions and Disk Dynamics for Snowlines and the C/N/O Ratios in Active Disks} \\
AAS Inner Solar Systems Meeting, Austin, TX, June 2017\\
Invited talk \\
\end{list2}

\begin{list2}
\item[] {\bf Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics} \\
Caltech Planetary Science Seminar, Pasadena, CA, February 2017\\
\end{list2}

\begin{list2}
\item[] {\bf Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics} \\
iPLEX Lunch Seminar, Los Angeles, CA, September 2016\\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
MIT Planetary Lunch Colloquium Series, Cambridge, MA, March 2016\\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
CfA Small Scale Seminar, Cambridge, MA, February 2016\\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
University of Michigan Astronomy Lunch Talk, Ann Arbor, MI, November 2015 \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
University of Chicago Exoplanet Journal Club, Chicago, IL, November 2015 \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
MIT Exoplanet Tea, Cambridge, MA, October 2015 \\
\end{list2}

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
Center for Integrative Planetary Science Planet and Star Formation Seminar, Berkeley, CA, September 2015 \\
\end{list2}

\vspace*{-.13in}
\begin{list2}
\item[] {\bf The Solar Wind}\\ 
Vienna Theory Lunch Club, TU Wien, Vienna, Austria, June 2009  \\
\end{list2}

\section{\sc Contributed Talks and Seminars}

@@

\begin{list2}
\item[] {\bf Minimum Core Masses for Giant Planet Formation} \\
CfA Exoplanet Pizza Lunch, Cambridge, MA, May 2015  \\
\end{list2}

\begin{list2}
\item[] {\bf Minimum Core Masses for Giant Planet Formation} \\
Star and Planet Formation in the Southwest, Oracle, AZ, March 2015  \\
\end{list2}

\begin{list2}
\item[] {\bf On the Minimum Core Mass for Giant Planet Formation} \\
CfA Exoplanet Pizza Lunch, Cambridge, MA, November 2013  \\
\end{list2}

\begin{list2}
\item[] {\bf On the Minimum Core Mass for Giant Planet Formation} \\
IAUS 299: Exploring the Formation and Evolution of Planetary Systems, Victoria, BC, June 2013  \\
\end{list2}

\section{\sc Posters}

\begin{list2}
\item[] {\bf C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion} \\
Extreme Solar Systems III, Waikoloa Village, HI, December 2015 \\
\end{list2}

\begin{list2}
\item[] {\bf On the Minimum Core Mass for Giant Planet Formation} \\
Protostars and Planets VI, Heidelberg, Germany, July 2013  \\
\end{list2}

\begin{list2}
\item[] {\bf The Structure and Stability of Atmospheres Accreting around Protoplanetary Cores} \\
Exoplanets in Multi-body Systems in the Kepler Era, Aspen, CO, February 2013 \\
\end{list2}

@@

\vspace*{-.13in}
\begin{list2}
\item[] {\bf Exact relativistic viscous fluid solutions in NHEK background} \\
APS April Meeting, Washington, DC, February 2010  \\
\end{list2}
